Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
use texttt for all Coq-bundled tools
mention the MIT license and why
Uniformize writing of sub-library.

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\coqmakefile}{coq\_makefile\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
\newcommand{\make}{\texttt{make}\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

Before the Ackermann sublibrary was moved from the Goedel package repository to the \Hydras repository, the Goedel package had around 7,000 specification LOC and 38,000 proof LOC. Figure~\ref{fig:genealogy} and Table~\ref{tbl:loc} thus reveal that the seemingly large Coq formalization of G\"{o}del's incompleteness theorem can be viewed as a modestly-sized proof on top of general libraries for, on the one hand, first-order logic, primitive recursive functions, and Peano Arithmetic (Ackermann), and on the other hand, prime numbers and their properties (Pocklington).

@@

\Hydras wants to provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it can give a concrete view of the mathematical content, not only through full proofs, but also through illuminating computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which may be also used to experiment with new maintenance techniques of the code and its documentation.

>>>>

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\coqmakefile}{\texttt{coq\_makefile}\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
\newcommand{\make}{\texttt{make}\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

Before the Ackermann sub-library was moved from the Goedel package repository to the \Hydras repository, the Goedel package had around 7,000 specification LOC and 38,000 proof LOC. Figure~\ref{fig:genealogy} and Table~\ref{tbl:loc} thus reveal that the seemingly large Coq formalization of G\"{o}del's incompleteness theorem can be viewed as a modestly-sized proof on top of general libraries for, on the one hand, first-order logic, primitive recursive functions, and Peano Arithmetic (Ackermann), and on the other hand, prime numbers and their properties (Pocklington).

@@

\Hydras wants to provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it can give a concrete view of the mathematical content, not only through full proofs, but also through illuminating computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which may be also used to experiment with new maintenance techniques of the code and its documentation. To facilitate easy dissemination and reuse, all code and documentation is available under the permissive MIT license.
